A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Add additional paragraphs (definitions)

>>>>

\paragraph*{Reduction procedure}

Bryant~\cite{BRYANT86, BRYANT92} described three transformation rules to reduce
a graph such that it still represents the same function as before.

For each constant function, there exists only a single terminal node representing
it, e.g. for Boolean functions, only two terminal nodes exist, representing
\textbf{0} and \textbf{1}, respectively. Hence, when transforming a given BDD,
eliminate all but one terminal node for each constant function and redirect all
edges accordingly, i.e. to the one remaining node for each constant function.

There may be duplicate nonterminal nodes present in a given BDD. Formally, a node
$d$ is a duplicate if $var(d) = var(n) \land lo(d) = lo(n) \land hi(d) = hi(n)$
holds for any other node $n$. If this is the case, $d$ can be eliminated and all
edges are redirected to $n$.

The third and thus last transformation rule deals with completely redundant 
nonterminal nodes. Intuitively, this rule should be straightforward: any node
having the same child on all outgoing edges is redundant because the actual value
of the variable does not change the result of the function. More formally, a
nonterminal node $n$ is redundant if $lo(n) = hi(n)$. Then, all incoming edges
of $n$ can be redirected to $lo(n)$ and $n$ can be deleted afterwards.
